% shtthesis, an unofficial LaTeX thesis template for ShanghaiTech University.
% Copyright (C) 2022 Li Rundong <rundong.001@gmail.com>
%
% This program is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <https://www.gnu.org/licenses/>

% graduate setup
% \documentclass[master, anonymous]{shtthesis}
\documentclass[master]{shtthesis}
\shtsetup{
  degree-name = {工学硕士},
  degree-name* = {Master~of~Science~in~Engineering},
  % secret-level = {白给},
  title = {三维环境中人和物体单目重建},
  title* = {3D Monocular Human-Object Reconstruction},
  keywords = {人-物交互，空间关系，单目重建，归一化流，三视视觉},
  keywords* = {Human-Object Interaction, Spatial Relation, Monocular Reconstruction, Normalizing Flow, 3D Vision},
  author = {霍超凡},
  author* = {Huo~Chaofan},
  institution = {上海科技大学信息科学与技术学院},
  institution* = {School~of~Information~Science~and~Technology\\%
                  ShanghaiTech~University},
  supervisor = {汪婧雅~助理教授},
  supervisor* = {Professor~Wang~Jingya},
  supervisor-institution = {上海科技大学信息科学与技术学院},
  discipline-level-1 = {计算机科学与技术},
  discipline-level-1* = {Computer~Science~and~Technology},
  bib-resource = {Biblio/ref.bib},
}

% `latex' and `shell' environments are adapted from `thuthesis'
\usepackage{listings}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{bm}
\usepackage{color}
\usepackage{booktabs}
\usepackage{bbding}
\usepackage{algorithm}  
\usepackage{algorithmicx} %或者\usepackage{algorithmic}
\usepackage{algpseudocode}
\newcommand\prompt{\textup{\$}}
\lstdefinestyle{lstStyleBase}{%
  basicstyle=\small\ttfamily,
  aboveskip=\medskipamount,
  belowskip=\medskipamount,
  lineskip=0pt,
  boxpos=c,
  showlines=false,
  extendedchars=true,
  upquote=true,
  tabsize=2,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  numbers=none,
  linewidth=\linewidth,
  xleftmargin=4pt,
  xrightmargin=0pt,
  resetmargins=false,
  breaklines=true,
  breakatwhitespace=false,
  breakindent=0pt,
  breakautoindent=true,
  columns=flexible,
  keepspaces=true,
  gobble=0,
  framesep=3pt,
  rulesep=1pt,
  framerule=1pt,
  frame=l,
  rulecolor=\color{ShtRed},
  backgroundcolor=\color{gray!5},
  stringstyle=\color{green!40!black!100},
  keywordstyle=\bfseries\color{blue!50!black},
  commentstyle=\slshape\color{black!60},
  escapeinside={`'},
}
\lstdefinestyle{lstStyleShell}{%
  style=lstStyleBase,
  language=bash}
\lstdefinestyle{lstStyleLaTeX}{%
  style=lstStyleBase,
  language=[LaTeX]TeX}
\lstnewenvironment{latex}{\lstset{style=lstStyleLaTeX}}{}
\lstnewenvironment{shell}{\lstset{style=lstStyleShell}}{}

\usepackage{hologo}
\ifluahbtex
  \usepackage{emoji}
\else
  \providecommand{\emoji}[1]{ \fbox{\emph{#1}} }
\fi

\usepackage{subcaption}
\usepackage{ctable}
\usepackage[list=off]{bicaption}
\captionsetup[figure][bi-second]{name=Figure}
\captionsetup[table][bi-second]{name=Table}

\makeatletter
  \def\ifundergraduate{\ifsht@undergraduate}
  \def\ifgraduate{\ifsht@graduate}
\makeatother

\begin{document}

\maketitle

\frontmatter
\input{chapters/abstract}

\makeindices

% \ifgraduate
% \begin{nomenclatures}
%   \header[单位]{符号}{说明}
%   \item[$\symup{{m^{2} \cdot s^{-2} \cdot K^{-1}}}$]{$R$}{the gas constant}
%   \item[$\symup{{m^{2} \cdot s^{-2} \cdot K^{-1}}}$]{$C_v$}{specific heat capacity at constant volume}
%   \item[$\symup{{m^{2} \cdot s^{-2} \cdot K^{-1}}}$]{$C_p$}{specific heat capacity at constant pressure}
%   \item[$\symup{{m^{2} \cdot s^{-2}}}$]{$E$}{specific total energy}
%   \item[$\symup{{kg \cdot m \cdot s^{-3} \cdot K^{-1}}}$]{$k$}{thermal conductivity}
%   \item[$\symup{{kg \cdot m^{-1} \cdot s^{-2}}}$]{$S_{ij}$}{deviatoric stress tensor}
%   \item[$\symup{{kg \cdot m^{-1} \cdot s^{-2}}}$]{$\tau_{ij}$}{viscous stress tensor}
%   \item[$\symup{{1}}$]{$\delta_{ij}$}{Kronecker tensor}
% \end{nomenclatures}

% \begin{nomenclatures}[缩写]
%   \header{缩写}{全称}
%   \item{CFD}{Computational Fluid Dynamics}
%   \item{CFL}{Courant-Friedrichs-Lewy}
%   \item{WENO}{Weighted Essentially Non-oscillatory}
%   \item{ZND}{Zel'dovich-von Neumann-Doering}
% \end{nomenclatures}

% \begin{nomenclatures}[算子 \& 说明]
%   \item{$\Delta$}{difference}
%   \item{$\nabla$}{gradient operator}
%   \item{$\delta^{\pm}$}{upwind-biased interpolation scheme}
% \end{nomenclatures}
% \fi

\mainmatter

\input{chapters/Chap_01_Intro}
\input{chapters/Chap_02_stackflow}
\input{chapters/Chap_03_stackflow_plus}
\input{chapters/Chap_04_super_2d}
\input{chapters/Chap_05_summary}

\makebiblio

\backmatter
\begin{acknowledgement}
在论文写作过程中，得到了许多人的帮助和支持，我在此要向他们表示由衷的感谢。首先，我要感谢我的导师汪婧雅教授，在整个研究过程中给予我耐心的指导和宝贵的建议，让我能够顺利完成毕业论文的撰写。

再次，我要感谢实验室的老师和同学们，他们在我遇到困难时给予了无私的帮助和支持，让我能够顺利完成实验和数据分析。同时，我也要感谢论文评阅老师和答辩委员会的专家们，他们的审阅和指导使我对自己的研究有了更深刻的认识。

最后，我要感谢我的家人和朋友们，在我研究生期间给予了我精神上的支持和鼓励，让我能够坚持下来并顺利完成学业。他们的陪伴和支持是我前进的动力和力量。

再次谨向以上所有给予我支持和帮助的人表示由衷的感谢！没有你们的支持，我的论文也不可能如此顺利完成。希望以后继续保持联系，共同进步！
\end{acknowledgement}

\ifgraduate
\begin{resume}
    \paragraph{姓名：} 霍超凡。
    \paragraph{教育经历：}
    \begin{itemize}
        \item 2017年-2021年，本科就读于山东大学的软件工程专业，获得学士学位。
        \item 2021年-2024年，硕士就读于上海科技大学的计算机科学与技术专业，获得硕士学位。
    \end{itemize}

    \paragraph{研究方向：}
    \begin{itemize}
        \item 2021年-2024年，三维空间中人和物体交互重建。
        \item 2024年-？，三维场景重建与编辑。
    \end{itemize}
    \paragraph{联系方式：}
    \begin{description}
        \item[电子邮箱：] huochf@shanghaitech.edu.cn
        \item[联系电话：] 18633656293
    \end{description}
\end{resume}

\begin{publications}
  \begin{description}
    \item[(已发表)] [一作] \textbf{Chaofan Huo}, Ye Shi, Yuexin Ma, Lan Xu, Jingyi Yu, Jingya Wang. StackFLOW: Monocular Human-Object Reconstruction by Stacked Normalizing Flow with Offset. In Proceedings of the Thirty-Second International Joint Conference on Artificial Intelligence, {IJCAI-23}.
    \item[(已投递)] [一作] \textbf{Chaofan Huo}, Ye Shi, Jingya Wang. Monocular Human-Object Reconstruction in the Wild. In ACM MultiMedia 2024.
  \end{description}
\end{publications}

\begin{publications*}
  \begin{description}
    \item[(已发表)] [一作] ***, ***, ***, ***, ***. ***. In Proceedings of the Thirty-Second International Joint Conference on Artificial Intelligence, {IJCAI-23}.
    \item[(已投递)] [一作] ***, ***, ***. ***. In ACM MultiMedia 2024.
  \end{description}
\end{publications*}

% \begin{patents}
%   专利申请或授权记录…… （非匿名环境）
% \end{patents}

% \begin{patents*}
%   专利申请或授权记录…… （匿名环境）
% \end{patents*}

% \begin{projects}
%   个人参与的科研项目、获奖情况…… （仅非匿名环境显示）
% \end{projects}
\fi

\end{document}
